---
title: "ncient {Redactum}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ncient}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup}
library(Redactum)
```

Abbreviated scientific name

The abbreviated name is derived from the scientific name. To create the
abbreviation, the first letter of the genus is taken, written in
uppercase, and followed by a period. The specific name is added after a
space in the scientific name.

Within the function, a condition is established. If the scientific name
refers to a species that is not specified under a particular genus, such
as Hydrolagus sp., or to multiple species within a genus, like
Hydrolagus spp., the name will not be abbreviated. However, if the
scientific name designates a specific species, it will be modified; for
instance, Hydrolagus melanophasma will be abbreviated to H.
melanophasma.

The function operates correctly with or without periods in
abbreviations, such as “sp” or “sp.”

The function requires defining:

    name A character string containing the scientific name.
    
It returns a character string containing the abbreviated scientific name.    

## Examples

Abbreviation used for scientific names.

```{r name}
ncient("Homo sapiens")

name <- "Hydrolagus melanophasma"
ncient(name)
```

Unspecified species within a genus, using the abbreviation “sp.” or “sp”
with or without a period.

```{r sp}
# With a period
ncient("Hydrolagus sp.")

# Without a period
ncient("Hydrolagus sp")
```

Unspecified species within a genus, using the abbreviation “spp.” or
“spp” with or without a period.

```{r spp}
# With a period
ncient("Hydrolagus spp.")

# Without a period
ncient("Hydrolagus spp")
```

